\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-08-06 syntactic-example.tex
Fix notation.

  \begin{minipage}[t]{0.4\linewidth}
  \small
\begin{align*}
  "Osig" &\coloneqq \goodWSig{\cdot}{w^+\ w\cdot\ \top\ \bot}{1} \\
  "sig"_1 &\coloneqq \goodSig{\cdot}{\nu^+ \ \nu\cdot \ {id_s} \ (\bW \ "Osig"[\pi_1])}{1}  \\
  "obj"_1 &\coloneqq \goodTerm{\cdot}{\mu^+ \ \mu\cdot \ {id_s} \ *}{\cL"sig"_1}\\
  \cC"sig"_1 &\coloneqq \goodType{\cdot}{\Sigma \ \top \ (\bW \ "Osig"[\pi_1]) }{} \\
  "sig"_2 &\coloneqq  \goodSig{\cdot}{\nu^+ \ "sig"_1 \ {id_s} \ El ("W" ("pjr" \ \pi_2))}{2} \\ 
  "O"_1 &\coloneqq {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ and thus }  \goodTerm{\cdot, \cC"sig"_1}{"O"_1}{El ("W" ("pjr" \pi_2))} \\
  "obj"_2 &\coloneqq \goodTerm{\cdot}{\mu^+ \ "obj"_1 \ "O"_1}{\cL"sig"_2} \\
  "sig"_2' &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top \cU)El ("pjr" \pi_2)}{} \\ 
  \cC"sig"_2 &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top (\bW \ "Osig"[\pi_1]))El ("W"("pjr" \pi_2)) }{} \\ 
  "sl"_1 &\coloneqq ((*, "W" ("pjr" ("pjl" \pi_2)) ), "pjr" \pi_2) \\ 
  & \text{ and thus }  \goodSeal{\cdot}{"sl"_1}{"sig"_2}{"sig"_2'} \\
  "pN"_1 &\coloneqq \goodType{\cdot, "sig"_2'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{} \\
  "handler"_1 &\coloneqq \goodTerm{\cdot, "sig"_2'}{\_}{\cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)} \\
  "sig"_3 &\coloneqq \goodSig{\cdot}{\nu^+ "sig"_2 \{"sl"_1\} \ \cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)}{3} \\ 
  "obj"_3 &\coloneqq \goodTerm{\cdot}{\mu^+~"obj"_2~"handler"_1}{\cL"sig"_3}\\
  "predT" &\coloneqq \Pi \ El ("W"("pjr" ("pjl"^2 \pi_2)))\ El ("W" ("pjr" ("pjl"^2  \pi_2)))[\pi_1] \\
  "pred"_1 &\coloneqq \goodTerm{\cdot, \cC "sig"_3}{\lambda ("Wrec" \_)}{"predT"} \\ 
  "sig"_4 &\coloneqq \nu^+ \ "sig"_3 \ \{id_s\} \ "predT" \\ 
  "obj"_4 &\coloneqq \goodTerm{\cdot}{\mu^+~"obj"_3~"pred"_1}{\cL"sig"_4}\\
  "sl"_4 &\coloneqq \goodSeal{\cdot}{\_}{"sig"_4}{"sig"_4'} \\
  "pN"_2 &\coloneqq \goodType{\cdot, "sig"_4'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{}
\end{align*}
\end{minipage}%
\begin{minipage}[t]{0.4\linewidth}
  \small
\begin{align*}
  "sig"_5 &\coloneqq \nu^+ \ "sig"_4 \ \{"sl"_4\} \  "pN"_2 \\ 
  "obj"_5 &: \goodTerm{\cdot}{\mu^+~"obj"_4~\_}{\cL"sig"_4}\\
  \\ 
  \text{Here we}&\text{ start to construct Family } "A"_2 \\ 
  "Nsig" &\coloneqq \goodWSig{\cdot}{w^+\ "Osig"\ \top \ \top}{2} \\ 
  "sig"_{11} &\coloneqq \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Nsig"[\pi_1])}{1} \\
  "inh"_1 &\coloneqq \goodInh{\cdot}{"inhov" \  "inhid" \ *}{"sig"_1}{"sig"_{11}}\\
  "O"_2 &\coloneqq {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ but }  \goodTerm{\cdot, \cC"sig"_{11}}{"O"_2}{El ("W" ("pjr" \pi_2))} \\
  "sig"_{21} &\coloneqq \nu^+ \ "sig"_{11} \ \{id_s\} (El (W (pjr p₂))) \\ 
  "inh"_2 &\coloneqq \goodInh{\cdot}{"inhov" \ "inh"_1 \ "O"_2}{"sig"_2}{"sig"_{21}}\\
  "S"_T &\coloneqq \Pi \ El ("W"("pjr"  ("pjl" \pi_2))) \ El ("W" ("pjr" ("pjl"  \pi_2)))[\pi_1] \\
  "sig"_{22} &\coloneqq \nu^+ \ "sig"_{21} \ \{id_s\} \ "S"_T \\ 
  "sig"_{21}' &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top \cU) (El ("pjr" \pi_2))}{} \\
  "sig"_{22}' &\coloneqq \Sigma "sig"_{21}' (\Pi \ El ("pjr"  ("pjl" \pi_2)) \  ...) \\
  "sl"_{22} &\coloneqq \goodSeal{\cdot}{\_}{"sig"_{22}}{"sig"_{22}'} \\ 
  "inh"_3 &\coloneqq \goodInh{\cdot}{\_}{"sig"_2}{"sig"_{22}} \\ 
  \uparrow^s &\coloneqq \goodTerm{\cdot, "sig"_{22}'}{\_}{"sig"_2'[\pi_1]} \\ 
  "pN"_3 &\coloneqq "pN"_1[(\pi_1, \uparrow^s)] \\ 
\end{align*}
  \end{minipage}

@@

Note that, since in our example there is only one type, the complicated debruijn indices $El("pjr" ("pjl" \pi_2)) $ in $"pN"_2$ and  $El("W"("pjr"("pjl"^2 \pi_2)))$ in "predT" are both referring to the type "N". The distinguishing difference is we have "W" (\ruleref{Ind-Type}) for the latter as "predT" is constructed in the context knowing the concrete definition of the inductive type, thus generally not inheritable. On the contrary,  $"pN"_2$ has as its context only $"N" : \cU$ and manifests its late-binding and its overridability for its former fields. \YZ{
  Maybe it is a good place to point out what El(pjr (pjl pi_2)) in pN_2 stands for
  and what El(W(pjr(pjl^2 pi_2))) in predT stands for.
}\EDJreply{Done.}\YZreply{
  I was actually alluding to how the type of pN_2 manifests late binding
  while the type of predT refers to the concrete signature of the
  inductive type.
}\YZreply{
  It’s good to be consistent in notations.  You later use * for products definition of pN_1, but you also use * as the term of type ($\bW$ $\sigma$) 
}\EDJreply{Sry. Now I attempt another try. I also change the above paragraph a bit to explain the details on sig₃, sig₄, and etc.
I also copy the comments in our slack to here to remind me about the changes.
Also let me paste the full example here for future reference: \\
% following is the body of pred₁
pred_ = Wrec ...  
  : Tm (⋅ ▹ 𝓒sig₃ ▹ (El (W (pjr (pjl (pjl π₂)))))) (El (W (pjr (pjl (pjl π₂)))))[π₁] \\
% we do lambda abstraction now
pred₁ = λ pred_ :   Tm (⋅ ▹ 𝓒sig₃) (∏ El (W (pjr (pjl (pjl π₂)))) (El (W (pjr (pjl (pjl p₂))))[π₁])) \\
% we can see that, the type of pred₁ is predT 
% now we construct sig4, this should not have any abstraction inside
sig₄ = ∨+ sig₃ id_s (∏ El (W (pjr (pjl (pjl π₂)))) (El (W (pjr (pjl (pjl π₂))))[π₁])) \\ 
% we omit the construction of obj₄
obj₄ : Tm ⋅ 𝓛sig₄ \\
% since pred is define in context 𝓒sig₃, we need to abstract 𝓒sig₄ into sig₄'
% again for later field,
sig₄' = 
  Σ (Σ ((Σ (Σ ⊤ 𝕌) (El (pjr π₂))) 𝓛(∨+ ⋅ (pN[π₁]))[sf sl₁])) 
    (∏ El (pjr (pjl (pjl π₂))) (El (pjr (pjl (pjl π₂)))[π₁]))
% and we have, omitting the detail construction 
sl₄ : Seal ⋅ sig₄ sig₄' \\
% pN₂ now is constructed in the context of the sealed context sig₄'
pN₂ = El (pjr (pjl π₂)) * El (pjr (pjl π₂)) : Ty (⋅ ▹ sig₄') 
% the product type \\ 
sig₅ = ∨+ sig₄ {sl₄} pN₂ \\ % the full example is in my gist last time I sent to you (Attempt 9), if you like it I can send the link again but note that the omission is still there and a lot of naming convention is different.
It seems that as you last night complained, I forget to add sig₄' causing problems.  Do I also need to make a note that those primed variables are always the result of abstraction?
}

>>>>

  \begin{minipage}[t]{0.4\linewidth}
  \small
\begin{align*}
  "Osig" &\coloneqq \goodWSig{\cdot}{w^+\ w\cdot\ \top\ \bot}{1} \\
  "sig"_1 &\coloneqq \goodSig{\cdot}{\nu^+ \ \nu\cdot \ {id_s} \ (\bW \ "Osig"[\pi_1])}{1}  \\
  "obj"_1 &\coloneqq \goodTerm{\cdot}{\mu^+ \ \mu\cdot \ {id_s} \ \star}{\cL"sig"_1}\\
  \cC"sig"_1 &\coloneqq \goodType{\cdot}{\Sigma \ \top \ (\bW \ "Osig"[\pi_1]) }{} \\
  "sig"_2 &\coloneqq  \goodSig{\cdot}{\nu^+ \ "sig"_1 \ {id_s} \ El ("W" ("pjr" \ \pi_2))}{2} \\ 
  "O"_1 &\coloneqq {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ and thus }  \goodTerm{\cdot, \cC"sig"_1}{"O"_1}{El ("W" ("pjr" \pi_2))} \\
  "obj"_2 &\coloneqq \goodTerm{\cdot}{\mu^+ \ "obj"_1 \ "O"_1}{\cL"sig"_2} \\
  "sig"_2' &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top \cU)El ("pjr" \pi_2)}{} \\ 
  \cC"sig"_2 &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top (\bW \ "Osig"[\pi_1]))El ("W"("pjr" \pi_2)) }{} \\ 
  "sl"_1 &\coloneqq ((\star, "W" ("pjr" ("pjl" \pi_2)) ), "pjr" \pi_2) \\ 
  & \text{ and thus }  \goodSeal{\cdot}{"sl"_1}{"sig"_2}{"sig"_2'} \\
  "pN"_1 &\coloneqq \goodType{\cdot, "sig"_2'}{El ("pjr" ("pjl" \pi_2)) \times El ("pjr" ("pjl" \pi_2))}{} \\
  "handler"_1 &\coloneqq \goodTerm{\cdot, "sig"_2'}{\_}{\cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)} \\
  "sig"_3 &\coloneqq \goodSig{\cdot}{\nu^+ "sig"_2 \{"sl"_1\} \ \cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)}{3} \\ 
  "obj"_3 &\coloneqq \goodTerm{\cdot}{\mu^+~"obj"_2~"handler"_1}{\cL"sig"_3}\\
  "predT" &\coloneqq \Pi \ El ("W"("pjr" ("pjl"^2 \pi_2)))\ El ("W" ("pjr" ("pjl"^2  \pi_2)))[\pi_1] \\
  "pred"_1 &\coloneqq \goodTerm{\cdot, \cC "sig"_3}{\lambda ("Wrec" \_)}{"predT"} \\ 
  "sig"_4 &\coloneqq \nu^+ \ "sig"_3 \ \{id_s\} \ "predT" \\ 
  "obj"_4 &\coloneqq \goodTerm{\cdot}{\mu^+~"obj"_3~"pred"_1}{\cL"sig"_4}\\
  "sl"_4 &\coloneqq \goodSeal{\cdot}{\_}{"sig"_4}{"sig"_4'} \\
  "pN"_2 &\coloneqq \goodType{\cdot, "sig"_4'}{El ("pjr" ("pjl" \pi_2)) \times El ("pjr" ("pjl" \pi_2))}{}
\end{align*}
\end{minipage}%
\begin{minipage}[t]{0.4\linewidth}
  \small
\begin{align*}
  "sig"_5 &\coloneqq \nu^+ \ "sig"_4 \ \{"sl"_4\} \  "pN"_2 \\ 
  "obj"_5 &: \goodTerm{\cdot}{\mu^+~"obj"_4~\_}{\cL"sig"_4}\\
  \\ 
  \text{Here we}&\text{ start to construct Family } "A"_2 \\ 
  "Nsig" &\coloneqq \goodWSig{\cdot}{w^+\ "Osig"\ \top \ \top}{2} \\ 
  "sig"_{11} &\coloneqq \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Nsig"[\pi_1])}{1} \\
  "inh"_1 &\coloneqq \goodInh{\cdot}{"inhov" \  "inhid" \ \star}{"sig"_1}{"sig"_{11}}\\
  "O"_2 &\coloneqq {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ but }  \goodTerm{\cdot, \cC"sig"_{11}}{"O"_2}{El ("W" ("pjr" \pi_2))} \\
  "sig"_{21} &\coloneqq \nu^+ \ "sig"_{11} \ \{id_s\} (El (W (pjr p₂))) \\ 
  "inh"_2 &\coloneqq \goodInh{\cdot}{"inhov" \ "inh"_1 \ "O"_2}{"sig"_2}{"sig"_{21}}\\
  "S"_T &\coloneqq \Pi \ El ("W"("pjr"  ("pjl" \pi_2))) \ El ("W" ("pjr" ("pjl"  \pi_2)))[\pi_1] \\
  "sig"_{22} &\coloneqq \nu^+ \ "sig"_{21} \ \{id_s\} \ "S"_T \\ 
  "sig"_{21}' &\coloneqq \goodType{\cdot}{\Sigma (\Sigma \top \cU) (El ("pjr" \pi_2))}{} \\
  "sig"_{22}' &\coloneqq \Sigma "sig"_{21}' (\Pi \ El ("pjr"  ("pjl" \pi_2)) \  ...) \\
  "sl"_{22} &\coloneqq \goodSeal{\cdot}{\_}{"sig"_{22}}{"sig"_{22}'} \\ 
  "inh"_3 &\coloneqq \goodInh{\cdot}{\_}{"sig"_2}{"sig"_{22}} \\ 
  \uparrow^s &\coloneqq \goodTerm{\cdot, "sig"_{22}'}{\_}{"sig"_2'[\pi_1]} \\ 
  "pN"_3 &\coloneqq "pN"_1[(\pi_1, \uparrow^s)] \\ 
\end{align*}
  \end{minipage}

@@

Note that, since in our example there is only one type, the complicated debruijn indices $El("pjr" ("pjl" \pi_2)) $ in $"pN"_2$ and  $El("W"("pjr"("pjl"^2 \pi_2)))$ in "predT" are both referring to the type "N". The distinguishing difference is we have "W" (\ruleref{Ind-Type}) for the latter as "predT" is constructed in the context knowing the concrete definition of the inductive type, thus generally not inheritable. On the contrary,  $"pN"_2$ has as its context only $"N" : \cU$ and manifests its late-binding and its overridability for its former fields. \YZ{
  Maybe it is a good place to point out what El(pjr (pjl pi_2)) in pN_2 stands for
  and what El(W(pjr(pjl^2 pi_2))) in predT stands for.
}\EDJreply{Done.}\YZreply{
  I was actually alluding to how the type of pN_2 manifests late binding
  while the type of predT refers to the concrete signature of the
  inductive type.
}\YZreply{
  It’s good to be consistent in notations.  You later use * for products definition of pN_1, but you also use * as the term of type ($\bW$ $\sigma$) 
}\EDJreply{Notation replaced. First * replaced with $\star$, second * replaced with $\times$}
\EDJreply{Sry. Now I attempt another try. I also change the above paragraph a bit to explain the details on sig₃, sig₄, and etc.
I also copy the comments in our slack to here to remind me about the changes.
Also let me paste the full example here for future reference: \\
% following is the body of pred₁
pred_ = Wrec ...  
  : Tm (⋅ ▹ 𝓒sig₃ ▹ (El (W (pjr (pjl (pjl π₂)))))) (El (W (pjr (pjl (pjl π₂)))))[π₁] \\
% we do lambda abstraction now
pred₁ = λ pred_ :   Tm (⋅ ▹ 𝓒sig₃) (∏ El (W (pjr (pjl (pjl π₂)))) (El (W (pjr (pjl (pjl p₂))))[π₁])) \\
% we can see that, the type of pred₁ is predT 
% now we construct sig4, this should not have any abstraction inside
sig₄ = ∨+ sig₃ id_s (∏ El (W (pjr (pjl (pjl π₂)))) (El (W (pjr (pjl (pjl π₂))))[π₁])) \\ 
% we omit the construction of obj₄
obj₄ : Tm ⋅ 𝓛sig₄ \\
% since pred is define in context 𝓒sig₃, we need to abstract 𝓒sig₄ into sig₄'
% again for later field,
sig₄' = 
  Σ (Σ ((Σ (Σ ⊤ 𝕌) (El (pjr π₂))) 𝓛(∨+ ⋅ (pN[π₁]))[sf sl₁])) 
    (∏ El (pjr (pjl (pjl π₂))) (El (pjr (pjl (pjl π₂)))[π₁]))
% and we have, omitting the detail construction 
sl₄ : Seal ⋅ sig₄ sig₄' \\
% pN₂ now is constructed in the context of the sealed context sig₄'
pN₂ = El (pjr (pjl π₂)) * El (pjr (pjl π₂)) : Ty (⋅ ▹ sig₄') 
% the product type \\ 
sig₅ = ∨+ sig₄ {sl₄} pN₂ \\ % the full example is in my gist last time I sent to you (Attempt 9), if you like it I can send the link again but note that the omission is still there and a lot of naming convention is different.
It seems that as you last night complained, I forget to add sig₄' causing problems.  Do I also need to make a note that those primed variables are always the result of abstraction?
}
